The User Behavior On Online Judge Website

### 2017-05-01 paper.tex
writing paper...

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{amsmath}
\graphicspath{{images/}}

@@

In 2016 Spring Festival, I solve some problems in Project Euler 
\footnote{In fact, I solve 70+ problems before my interest fade.}, 
which may be most famous online judge 
in Internet except Leetcode. I have noticed the interesting data structure related with rank and difficulty.
But I lacked enough powerful statistic tool to process and model it. 
In fact, I model it as a ordinary least squard which is not understood by me in the time. In the naive period,
linear regression model seems like a poor black box model that often be meeted in Machine Learning algorithm.

@@

and define $D2$ which follow order of the number of solved:

@@

$$
S_j = \sum_{i=1}^n s_{ij}
$$

Our data is only the a obseration of statistic $S_j$ exactly. It looks like:

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath,amssymb}
\graphicspath{{images/}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\E}{\mathbb{E}}

@@

In 2016 Spring Festival, I solve some problems in Project Euler 
\footnote{In fact, I solve 70+ problems before my interest fade.}, 
which may be most famous online judge 
in Internet except Leetcode. I have noticed the interesting data structure related with rank and difficulty.
But I lacked enough powerful statistic tool to process and model it. 
In fact, I model it as a ordinary least square which is not understood by me in the time. In the naive period,
linear regression model seems like a poor black box model that often be meeted in Machine Learning algorithm.

@@

and define $D_2$ which follow order of the number of solved:

@@

\[
S_j = \sum_{i=1}^n s_{ij}
\]

We have only data that is once obseration of statistic $S_j$ exactly. It looks like:

\begin{figure}[h]

\centering

\subfigure[Solved number series]{\label{fig:a}\includegraphics[width=0.49\linewidth]{solved-seq1.png}}
\subfigure[Log solved number series]{\label{fig:b}\includegraphics[width=0.49\linewidth]{solved-seq2.png}}

\end{figure}

The data is scraped from Project Euler \footnote{Project Euler website: https://projecteuler.net/archives }
, my problem answers, crawler program and basis analysis is hosted on GitHub \footnote{https://github.com/yiyuezhuo/euler }
This is a screenshot for Project Euler website:

\includegraphics[scale=0.55]{euler-oj.png}

Given $n_1,n_2,p$, we can determine a model like we talk above. 
We can specify these values througn minimizing the squard loss function:

\[
\min_{n_1,n_2,p} \sum_{j=1}^N (S^*_j - \E(S_j))^2
\]

In which $S^*_j$ is real value, $S_j$ is random variable defined by model and $n_1,n_2,p$

We would like a model taking more statistic manner instead of only fitting function. 
Thus we assume that the model is \textit{real} 
\footnote{As so often happens, some funny Econometric model claim they're real, 
otherwise statistic model will reduce to awkward explore method.} 
and add a convenient noise term  $\epsilon_j$  to all $S_j$ to let our model can generate(sample) 
any possible sequence \footnote{Anyway, a pure noise model can do it too.}.

\begin{align*}
S_j = \sum_{i=1}^n s_{ij} + \epsilon_j \\
\epsilon_j \sim F \quad i.i.d 
\end{align*}

In which $F$ is a integer distribution that can take binomial distribution or something.

\[
\E(S_j) = \sum_{i=1}^n \E(s_{ij}) + \E(\epsilon_j) = \sum_{i=1}^{n_1} p^j + \sum_{i=n_1+1}^n p^{r(j)}
= n_1 p^j + n_2 p^{r(j)}
\]

and apply least expectation loss rule, very frequentist:

\[
\hat{n_1},\hat{n_2},\hat{p} = \argmin_{n_1,n_2,p} \E\sum_{j=1}^N (S_j - \hat{S_j})^2
\]

In which $\hat{S_j} = \E(S_j | \hat{n_1},\hat{n_2},\hat{p})$.

Unfortunately, this nonlinear form can't be transformed to linear form directly. Temporarily, 
we constrain $n_2 = 0$, then $n_1 = n$, then the $\E(S_j)$ reduce to:

\[
\E{S_j} = n p^j
\]

and

\[
\log \E(S_j) = \log n + j \log(p)
\]

Well, so we can estimate $n,p$ by estimating $\log(n),\log(p)$ by running ordinary least square method to 
minimize the objective function \footnote{Alrough I feel that this conversion is not strict true, since
it assign different weights on every data point.}:

\[
\min_{\hat{n},\hat{p}} \sum_{j=1}^N ( S_j - (\log(\hat{n}) + j \log(\hat{p})) )
\]

For the real data, the estimated results are:

\[
\hat{n} = 95132.76 \quad \hat{p} = 0.98002
\]

The $\hat{n}$ looks too small and $\hat{p}$ looks too big as we notice the quick fall of sequence head that
can not be expressed the too small $\hat{p}$ as the fit graph illustrate:

\includegraphics[scale=0.55]{simple-fit.png}

Since the fitting is dominated by the tail data, the rift implies that our model is too weak to express 
the mechanism behind the data.

We can verify this by to regress data chunks separately, 
obviousily if the model is true, $\hat{p}$ will only change little subject to random noise. 
Below results are obtained by taken first $1/10$ data and last $9/10$ data separately:

\[
\hat{p_1} = 0.9275 \quad \hat{p_2} = 0.9824
\]

% Let us merge the two fitting result into a unique figure:
